\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/badusb.tex

	\item\underline{Video Capture Card} converts DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by the Single Board Computer (i.e., an embedded computer).

@@

	\begin{tabular}{ll}
	\mycircled{1} Victim's Devices    &\mycircled{2}\tool\\
	\mycircled{3} Attacker's Remote PC
	\end{tabular}

>>>>

	\item\underline{Video Capture Card} converts DisplayPort signal into compatible data, which is later processed by the Single Board Computer (i.e., an embedded computer).

@@

	\begin{tabular}{ll}
	\circled[text=white,fill=myyellow]{\footnotesize{1}} Victim's Devices    &\circled[text=white,fill=myyellow]{\footnotesize{2}}~\tool\\
	\circled[text=white,fill=myyellow]{\footnotesize{3}} Attacker's Remote PC
	\end{tabular}
